---
title: "Statistical-analysis_Angular_distances"
author: "Filip Turoboś"
date: "31.03.2022"
output: html_document
---

# Analysis of angular distances

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(boot) 
library(ggplot2)
library(scales)
library(dplyr)
library(ggpubr)
```

Functions to generate confidence intervals for the mean/standard deviation (assuming normality and not):
```{r}
bootmean<- function(data, indices) { 
  d <- data[indices] 
    return(mean(d))
} 

bootsd<- function(data, indices) { 
  d <- data[indices] 
    return(sd(d))
}

bootvar<- function(data, indices) { 
  d <- data[indices] 
    return(var(d))
} 

bootstrapCI<- function(data0, reps,alpha,statistic = 'mean'){

  if(statistic == 'mean'){
    results <- boot(data=data0, statistic=bootmean, R=reps)
    statval <- mean(data0)
  }
  if(statistic == 'variance'){
    results <- boot(data=data0, statistic=bootvar, R=reps)
    statval <- var(data0)
  }
  if(statistic == 'standard_deviation'){
    results <- boot(data=data0, statistic=bootsd, R=reps)
    statval <- sd(data0)
  }
print(results) 
plot(results)
a<-boot.ci(results, type=, conf=1-alpha)
a
print(paste(statistic,' of provided sample without normality assumption: ', toString(statval)))
print(paste(statistic,' confidence interval for sample: [', toString(a$normal[2:3]),']'))
}

generate_confidence_intervals_for_means<-function(sample,alpha,normality = TRUE, seed = 2121){ 
if(normality){
  print(paste("Mean of provided sample under normality assumption: ", toString(mean(sample))))
degrees.of.freedom <- length(sample) - 1
t.score <- qt(p=alpha/2, df=degrees.of.freedom, lower.tail=F)
sample.standard.error <- sd(sample)/sqrt(length(sample))*t.score
print(paste("Confidence interval for sample: [ ",toString(mean(sample)-sample.standard.error),' ',toString(mean(sample)+sample.standard.error),' ]'))
}
else{
  set.seed(seed)
  bootstrapCI(sample,5000,alpha)
} 
}
```

```{r}
generate_confidence_intervals_for_variance<-function(sample,alpha,normality = TRUE, seed = 2121){
if(normality){
print(paste("Variance of provided sample under normality assumption: ", toString(var(sample))))
degrees.of.freedom <- length(sample) - 1
t.score <- qchisq(p=alpha/2, df=degrees.of.freedom, lower.tail =T)
t.score2 <- qchisq(p=1-alpha/2, df=degrees.of.freedom, lower.tail = T)
sample.upperestimate <- var(sample)*degrees.of.freedom/t.score
sample.lowerestimate <- var(sample)*degrees.of.freedom/t.score2
print(paste("Confidence interval for sample: [ ",toString(sample.lowerestimate),' ',toString(sample.upperestimate),' ]'))
}
else{
  set.seed(seed)
  bootstrapCI(sample,5000,alpha,statistic = 'variance')
}
}

generate_confidence_intervals_for_standard_deviation<-function(sample,alpha,normality = TRUE, seed = 2121){
  if(normality){
  print(paste("Standard deviation of provided sample under normality assumption: ", toString(sd(sample))))
degrees.of.freedom <- length(sample) - 1
t.score <- qchisq(p=alpha/2, df=degrees.of.freedom)
t.score2 <- qchisq(p=1-alpha/2, df=degrees.of.freedom)
sample.upperestimate <- sqrt(var(sample)*degrees.of.freedom/t.score)
sample.lowerestimate <- sqrt(var(sample)*degrees.of.freedom/t.score2)
print(paste("Confidence interval for sample: [ ",toString(sample.lowerestimate),' ',toString(sample.upperestimate),' ]'))
}
else{
  set.seed(seed)
  bootstrapCI(sample,5000,alpha,statistic = 'standard_deviation')
}
}
```


Tools to generate histograms:

```{r}
histogram_gen<-function(dane, discard_percentage, binns = 25, title, axis_desc, quant=1, bootstrap_mean, bootstrap_left, bootstrap_right){

  data_frame(val = dane[dane < quantile(dane,quant)]) %>%ggplot(. , aes(val))+
geom_histogram(col="black",
fill="lightcoral",
bins=binns
)+
scale_x_continuous(breaks=pretty_breaks(10)) +
scale_y_continuous(breaks=pretty_breaks(5)) +
geom_vline(xintercept=bootstrap_mean, col="red")+
geom_vline(xintercept=bootstrap_left, col="blue")+
geom_vline(xintercept=bootstrap_right, col="blue")+
ggtitle(title) +
xlab(axis_desc)+
theme(plot.title = element_text(hjust = 0.5))
}
```

```{r}

normality_testing <-function(dane){
qqnorm(((dane-mean(dane))/sd(dane)))
qqline(((dane-mean(dane))/sd(dane)))

shapiro.test(dane)
}
```

## Quaternary-Oxford and Oxford-Callovian

Angular distances between Quaternary-Oxford and Oxford-Callovian.

```{r}
MQ_df<-read.csv("quaternary_oxford_aalen_good_columns_output_01.txt", header = TRUE, sep = ";", dec=".")
```


Analysis of angular distance expressed in degree units - we filter the data set:

```{r}
Angular_distances_QO_OC <- select(MQ_df,AngularDistance_normals) %>% filter(.,AngularDistance_normals<10)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Quaternary-Oxfordian vs. \n Oxfordian-Callovian', binns = 20, axis_desc = 'degrees', quant = 1, bootstrap_mean=1.684, bootstrap_left=1.482, bootstrap_right=1.891)
```


We investigate the mean. Note that the data is normally distributed:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:

```{r}
int_for_means<-generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

We calculated the 95% interval for the mean. The sample mean:


```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```

Confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=421)
```

The calculated 95% interval for the variance is 
 [1.581,  3.194], so after removing outliers the tested data behave in a stable manner. The sample variance is:

```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```

The confidence interval for the standard deviation:

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

The calculated sample standard deviation:

```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.


```{r}
Angular_distances_QO_OC_log_transformed <- mutate(Angular_distances_QO_OC,logdist =log(AngularDistance_normals+1))$logdist
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distance+1): Quaternary-Oxfordian vs.\n Oxfordian-Callovian', axis_desc ='log(degrees+1)' ,quant = 1 , binns=20,bootstrap_mean=0.867, bootstrap_left=0.806, bootstrap_right=0.930)
```


We investigate the mean. The transformed data are still not normal but the deviations from normality are smaller:

```{r}
qqnorm(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))
qqline(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))

shapiro.test(Angular_distances_QO_OC_log_transformed)
```


We conduct two analyses: with normality assumption (which does not hold) and without. We start with a confidence interval for the mean using bootstrap methods, which do not require normality:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

If we assume normality, the obtained confidence interval would be:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```


The difference is negligible.

Likewise, we can generate the confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```

The 95% confidence interval for the variance shows that the log-transformation reduces the dispersion of the variable. Variance of the log-transformed data is:

```{r}
var(Angular_distances_QO_OC_log_transformed)
```


The confidence interval determined using the (not true) normality assumption would be similar:
```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```

We generate the confidence interval for the st. dev. using bootstrap methods: 

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```


The sample log-transformed st. dev.:
```{r}
sd(Angular_distances_QO_OC_log_transformed)
```

#Improved histograms

```{r}
h1<-histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Quaternary-Oxfordian vs. \n Oxfordian-Callovian', binns = 20, axis_desc = 'degrees', quant = 1, bootstrap_mean=1.684, bootstrap_left=1.482, bootstrap_right=1.891)
```

```{r}
h1
```

```{r}
h2<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distances+1): Quaternary-Oxfordian vs. \n Oxfordian-Callovian', axis_desc = 'log(degrees+1)' , quant = 1 , binns=20, bootstrap_mean=0.867, bootstrap_left=0.806, bootstrap_right=0.930)
```

```{r}
h2
```


## Quaternary-Oxford i Bajocian-Aalenian

Angular distance between contacts: Quaternary-Oxford and Bajocian-Aalenian.

```{r}
MQ_dft<-read.csv("quaternary_oxford_aalen_good_columns_output_02.txt", header = TRUE, sep = ";", dec=".")
```

Analysis of angular distance expressed in degree units - we filter the data set:


```{r}
Angular_distances_QO_OC <- select(MQ_dft,AngularDistance_normals) %>% filter(.,AngularDistance_normals<15)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Quaternary-Oxfordian vs.\n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 30, axis_desc = 'degrees',quant = 1,bootstrap_mean=2.165, bootstrap_left=1.942, bootstrap_right=2.488)
```


We first investigate the mean. The data are not normal:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:
```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

We calculated the 95% confidence interval for the mean. The sample mean is:
```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```


Likewise, we can calculate the confidence interval for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=421)
```


We obtained the 95% confidence interval for the variance. The sample variance is:
```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```


We can determine the confidence interval for the st. dev.:

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

The calculated sample st. dev.:
```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.


```{r}
Angular_distances_QO_OC_log_transformed <- mutate(Angular_distances_QO_OC,logdist =log(AngularDistance_normals+1))$logdist
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distances+1): Quaternary-Oxfordian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log(degrees+1)' ,quant = 1 , binns=20,bootstrap_mean=0.967, bootstrap_left=0.894, bootstrap_right=1.041)
```


First, we investigate the mean. The transformed data are not normal, but it has improved a bit.
```{r}
normality_testing(Angular_distances_QO_OC_log_transformed)
```
Analysis without normality assumption.

We generate the confidence interval for the mean using bootstrap methods that do not require normality assumptions:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

If we assume normality, the confidence interval would almost not differ:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```

The difference is negligible.

Likewise, we can determine the confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```

The 95% confidence interval for the variance shows that the log-transformation reduces the dispersion of the variable. 
Unfortunately, it is difficult to transform this interval by an inverse transformation. The variance of the log-transformed data is:

```{r}
var(Angular_distances_QO_OC_log_transformed)
```

The confidence interval determined using (not true) normality assumption would be neglibly more precise:
```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```

We generate confidence intervals for the st. dev. using bootstrap methods:
```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

The sample st. dev. of log-transformed data is:
```{r}
sd(Angular_distances_QO_OC_log_transformed)
```
#Improved histograms

```{r}
h3<-histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Quaternary-Oxfordian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 30, axis_desc = 'degrees', quant = 1, bootstrap_mean=2.165, bootstrap_left=1.842, bootstrap_right=2.488)
```

```{r}
h3
```


```{r}
h4<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distance+1): Quaternary-Oxfordian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log(degrees+1)' ,quant = 1 , binns=20, bootstrap_mean=0.967, bootstrap_left=0.894, bootstrap_right=1.041)
```

```{r}
h4
```

## Oxford-Callovian and Bajocian-Aalenian

We will analyze angular distances between contacts: Oxford-Callovian and Bajocian-Aalenian.

```{r}
MQ_dft<-read.csv("quaternary_oxford_aalen_good_columns_output_12.txt", header = TRUE, sep = ";", dec=".")
```

Analysis of angular distance expressed in degree units - we filter the data set:


```{r}
Angular_distances_QO_OC <- select(MQ_dft,AngularDistance_normals) %>% filter(.,AngularDistance_normals<15)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Oxfordian-Callovian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'degrees' ,quant = 1,bootstrap_mean=1.167, bootstrap_left=0.951, bootstrap_right=1.383)
```


First, we investigate the mean. The data are not normal:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

We calculated the 95% interval for the mean. The sample mean is:
```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```


Likewise, we can determine confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=421)
```


We obtained the 95% confidence interval for the variance. The sample variance is:

```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```

We can also determine the confidence interval for the st. dev.:
```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

The calculated sample st. dev.:
```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.



```{r}
Angular_distances_QO_OC_log_transformed <- mutate(Angular_distances_QO_OC,logdist =log(AngularDistance_normals+1))$logdist
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distance+1): Oxfordian-Callovian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log(degrees+1)',quant = 1 , binns=20,bootstrap_mean=0.625, bootstrap_left=0.563, bootstrap_right=0.687)
```



First, we investigate the mean. The transformed data are still not normal.

```{r}
normality_testing(Angular_distances_QO_OC_log_transformed)
```
Analysis without normality assumption.
We generate the confidence interval for the mean using bootstrap methods that do not require normality assumptions:


```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

If we assume normality, the obtained confidence interval would almost not differ:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```
The difference is negligible.



Likewise, we can determine the confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```


The 95% confidence interval for the variance shows that the log-transformation reduces the dispersion of the variable. 
Unfortunately, it is difficult to transform this interval by an inverse transformation. Applying the function  $x\mapsto e^{x}-1$ will generate a meaningless confidence interval:
```{r}
a<-c(0.162148623016129, 0.292815497570269)
c(exp(a[1])-1, exp(a[2])-1)
```


The variance of log-transformed data:
```{r}
var(Angular_distances_QO_OC_log_transformed)
```

The confidence interval determined using (not true) normality assumption would be more precise:
```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```

Using bootstrap methods, we generate confidence intervals for the st. dev.:

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```


The standard deviation of log-transformed data:
```{r}
sd(Angular_distances_QO_OC_log_transformed)
```
#Improved histograms

```{r}
h5<-histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Angular distances: Oxfordian-Callovian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'degrees', quant = 1, bootstrap_mean=1.167, bootstrap_left=0.951, bootstrap_right=1.383)
```

```{r}
h5
```

```{r}
h6<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'log(angular distance+1): Oxfordian-Callovian vs. \n Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log(degrees+1)' ,quant = 1 , binns=20, bootstrap_mean=0.625, bootstrap_left=0.563, bootstrap_right=0.687)
```

```{r}
h6
```


## Quaternary/Oxford-Oxford/Callovian minus Oxford/Callovian-Bajocian/Aalenian

Arithmetic differences: Quaternary/Oxford-Oxford/Callovian minus Oxford/Callovian-Bajocian/Aalenian

```{r}
difmap1a<-read.csv("quaternary_oxford_aalen_good_columns_output_01.txt", header = TRUE, sep = ";", dec=".")
difmap1b<-read.csv("quaternary_oxford_aalen_good_columns_output_02.txt", header = TRUE, sep = ";", dec=".")
```

Analysis of angular distance expressed in degree units - we filter the data set:


```{r}
Angular_distances_QO_OC <- (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals)) %>% filter(.,abs(AngularDistance_normals)<15)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'angular difference',quant = 1,bootstrap_mean=-0.123, bootstrap_left=-0.337, bootstrap_right=0.094)
```



First, we investigate the mean. The data are not normal:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:
```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```


We calculated the 95% interval for the mean. The sample mean is:
```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```



Likewise, we can determine the confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```


The sample variance is:

```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```

We determine the confidence interval for the st. dev.:

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```
The calculated sample st. dev.:
```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.

In case of difference, the difference of logarithms is the logarithm of a quotient.


```{r}
difmap1a$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```
```{r}
difmap1b$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```
```{r}
Angular_distances_QO_OC_log_transformed<- (select(filter(difmap1a,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist - (select(filter(difmap1b,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist
```

```{r}
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian vs. \n Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log angular difference' ,quant = 1 , binns=20,bootstrap_mean=-0.038, bootstrap_left=-0.078, bootstrap_right=0.003)
```


We investigate the mean. The transformed data are more similar to normality but the hypothesis about normality cannot be considered.

```{r}
normality_testing(Angular_distances_QO_OC_log_transformed)
```

Analysis without normality assumption. We generate the confidence interval for the mean:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

Likewise, we can determine the confidence interval for the variance and st. dev.:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```
#Improved histograms

```{r}
h7<-histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus \n Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'angular difference',quant = 1, bootstrap_mean=-0.123, bootstrap_left=-0.337, bootstrap_right=0.094)

```

```{r}
h7
```

```{r}
h8<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus \n Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc ='log angular difference' ,quant = 1 , binns=20, bootstrap_mean=-0.038, bootstrap_left=-0.078, bootstrap_right=0.003)
```

```{r}
h8
```


## Quaternary/Oxford-Oxford/Callovian minus Oxford/Callovian-Bajocian/Aalenian

Arithmetic differences: Quaternary/Oxford-Oxford/Callovian minus Oxford/Callovian-Bajocian/Aalenian

```{r}
difmap1a<-read.csv("quaternary_oxford_aalen_good_columns_output_01.txt", header = TRUE, sep = ";", dec=".")
difmap1b<-read.csv("quaternary_oxford_aalen_good_columns_output_12.txt", header = TRUE, sep = ";", dec=".")
```

Analysis of angular distance expressed in degree units - we filter the data set:


```{r}
Angular_distances_QO_OC <- (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals)) %>% filter(.,abs(AngularDistance_normals)<15)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian vs. \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'angular difference' ,quant = 1,bootstrap_mean=1.031, bootstrap_left=0.675, bootstrap_right=1.381)
```



First, we investigate the mean. The data are not normal:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:
```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```


We obtained the 95% interval for the mean. The sample mean is:
```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```



We can determine the confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=421)
```



We obtained the 95% interval for the variance. The sample variance is:

```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```


The confidence interval for the st. dev:
```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```
Obliczone odchylenie standardowe z próbki:
```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.


In case of difference, the difference of logarithms is the logarithm of a quotient.


```{r}
difmap1a$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```

```{r}
difmap1b$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```
```{r}
Angular_distances_QO_OC_log_transformed<- (select(filter(difmap1a,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist - (select(filter(difmap1b,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist
```

```{r}
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian vs. \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc ='log angular difference' ,quant = 1 , binns=20,bootstrap_mean=0.311, bootstrap_left=0.238, bootstrap_right=0.383)
```



First, we investigate the mean. The transformed data are similar to normal data. We will do analysis using the assumption of normality and without.

```{r}
qqnorm(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))
qqline(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))

shapiro.test(Angular_distances_QO_OC_log_transformed)
```
With normality assumption. We generate the confidence interval for the mean: 

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```


Without this assumption using bootstrap methods we obtain the following intervals:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2033)
```


The confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=421)
```

Confidence interval for the st. dev. determined using the normality assumption

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```



Analogous calculations for the variance and standard deviation without normality assumptions are presented below:
```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```

#Improved histograms

```{r}
h9<- histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'angular difference',quant = 1, bootstrap_mean=1.031, bootstrap_left=0.675, bootstrap_right=1.381)
```

```{r}
h9
```

```{r}
h10<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log angular difference' ,quant = 1 , binns=20, bootstrap_mean=0.311, bootstrap_left=0.238, bootstrap_right=0.383)
```

```{r}
h10
```

## Quaternary/Oxford-Bajocian/Aalenian minus Oxford/Callovian-Bajocian/Aalenian

Arithmetic differences: Quaternary/Oxford-Bajocian/Aalenian minus Oxford/Callovian-Bajocian/Aalenian

```{r}
getwd()
```

```{r}
difmap1a<-read.csv("quaternary_oxford_aalen_good_columns_output_02.txt", header = TRUE, sep = ";", dec=".")
difmap1b<-read.csv("quaternary_oxford_aalen_good_columns_output_12.txt", header = TRUE, sep = ";", dec=".")
```

Analysis of angular distance expressed in degree units - we filter the data set:




```{r}
Angular_distances_QO_OC <- (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals)) %>% filter(.,abs(AngularDistance_normals)<15)
histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian vs. \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = 'angular difference',quant = 1,bootstrap_mean=1.008, bootstrap_left=0.707, bootstrap_right=1.308)
```



First, we investigate the mean. The data are not normal:

```{r}
normality_testing(Angular_distances_QO_OC$AngularDistance_normals)
```
It is visible on the quantile plots and in the p-value in the Shapiro-Wilk test is smaller than $10^{-15}$.

We generate the confidence interval using bootstrap methods that do not require normality assumptions:
```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

The sample mean:
 
```{r}
mean(Angular_distances_QO_OC$AngularDistance_normals)
```


Confidence interval for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=421)
```

The sample variance:

```{r}
var(Angular_distances_QO_OC$AngularDistance_normals)
```

We can determine the confidence interval for the standard deviation:

```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC$AngularDistance_normals,0.05,normality =FALSE, seed=2021)
```

The calculated sample standard deviation:
```{r}
sd(Angular_distances_QO_OC$AngularDistance_normals)
```

Analysis of transformed data using $x\mapsto ln(x+1)$.




In case of difference, the difference of logarithms is the logarithm of a quotient.

```{r}
difmap1a$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```
```{r}
difmap1b$Angdistnormdiff<-  (select(difmap1a,AngularDistance_normals)-select(difmap1b,AngularDistance_normals))$AngularDistance_normals
```
```{r}
Angular_distances_QO_OC_log_transformed<- (select(filter(difmap1a,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist - (select(filter(difmap1b,abs(Angdistnormdiff)<15),AngularDistance_normals) %>% mutate(.,logdist = log(1+AngularDistance_normals)))$logdist
```

```{r}
histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Oxfordian/Callovian minus \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc ='log angular difference' ,quant = 1 , binns=20, bootstrap_mean=0.349, bootstrap_left=0.284, bootstrap_right=0.414)
```

First, we investigate the mean. The transformed data are similar to normal data. We will do analysis using the assumption of normality and without.

```{r}
qqnorm(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))
qqline(((Angular_distances_QO_OC_log_transformed-mean(Angular_distances_QO_OC_log_transformed))/sd(Angular_distances_QO_OC_log_transformed)))

shapiro.test(Angular_distances_QO_OC_log_transformed)
```

We will start with assumption of normality. We generate the confidence interval for the mean:

```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```
Confidence intervals for the variance:

```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=421)
```

The confidence interval for the standard deviation estimated using the normality assumption:
```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =TRUE, seed=2021)
```


Analogous calculations without normality assumptions do not deviate from their counterparts that assume normality:
```{r}
generate_confidence_intervals_for_means(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```





```{r}
generate_confidence_intervals_for_variance(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=421)
```
```{r}
generate_confidence_intervals_for_standard_deviation(Angular_distances_QO_OC_log_transformed,0.05,normality =FALSE, seed=2021)
```


#Improved histograms

```{r}
h11<- histogram_gen(Angular_distances_QO_OC$AngularDistance_normals, title = 'Differences in angular distances: \n Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds minus \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', binns = 20, axis_desc = ' angular difference',quant = 1, bootstrap_mean=1.008, bootstrap_left=0.707, bootstrap_right=1.308)
```

```{r}
h11
```

```{r}
h12<-histogram_gen(Angular_distances_QO_OC_log_transformed, title = 'Differences in log angular distances: \n Quaternary/Oxfordian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds minus \n Oxfordian/Callovian-Częstochowa Ore-Bearing \n Clay Fm/Kościeliska Beds', axis_desc = 'log angular difference' ,quant = 1 , binns=20, bootstrap_mean=0.349, bootstrap_left=0.284, bootstrap_right=0.414)
```

```{r}
h12
```


#Summary histograms START

```{r}
summary_histograms<- ggarrange(h1, h2, h3, h4, h5, h6,  ncol=2, nrow=3, labels=c("A", "B", "C", "D", "E", "F"), common.legend = FALSE)
```

```{r}
summary_histograms
```

```{r}
tiff("summary_histograms.tif", units="in", width=10, height=7, res=300)
summary_histograms
dev.off()
```
#Summary histograms STOP

#Summary histograms DIFFERENCE START

```{r}
summary_histograms_diff<- ggarrange(h7, h8, h9, h10, h11, h12, ncol=2, nrow=3, labels=c("A", "B", "C", "D", "E", "F"), common.legend = FALSE)
```

```{r}
summary_histograms_diff
```

```{r}
tiff("summary_histograms_diff.tif", units="in", width=10, height=7, res=300)
summary_histograms_diff
dev.off()
```
#Summary histograms DIFFERENCE STOP
